### 2020-06-27 system-model.tex
:pencil: Update algorithm input
:pencil: Alternating optimization

\begin{section}{Single-User Optimization}
	Consider a single-user waveform and IRS optimization problem where $\boldsymbol{\alpha}=\boldsymbol{1}^{N \times 1}$. We characterize the rate-energy region through a current maximization problem subject to transmit power, rate, and IRS constraints
	\begin{maxi!}
			{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho}{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)}{\label{op:su}}{}
			\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
			\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert(h_{D,n}+\boldsymbol{v}_n^H\boldsymbol{\phi})w_{I,n}\rvert^2}{\sigma_n^2}\right)} \ge \bar{R}}
			\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}
			\addConstraint{0 \le \rho \le 1}
		\end{maxi!}
	Problem \ref{op:su} is intricate due to the non-convex objective function with coupled variables. In the next section, we propose waveform and phase shift design algorithms for frequency-flat and frequency-selective IRS, respectively.

	\begin{subsection}{Frequency-Selective IRS}
		Each element in frequency-selective IRS is expected to provide subband-dependent reflection coefficients. Hence, $\boldsymbol{\phi}_n$ replaces $\boldsymbol{\phi}$ in \ref{op:su} and the IRS has a total degree of freedom (DoF) of $NL$. Note that $\lvert{(h_{D,n}+\boldsymbol{v}_n^H\boldsymbol{\phi}_n)w_{I,n}}\rvert \le \lvert{h_{D,n}w_{I,n}}\rvert+\lvert{\boldsymbol{v}_n^H\boldsymbol{\phi}_n w_{I,n}}\rvert$ where the equality holds when the direct and IRS-aided links are aligned. Therefore, we choose the phase shift of element $l$ at subband $n$ as
		\begin{equation}\label{eq:theta}
			\theta_{n,l}^\star = \angle{h}_{D,n} - \angle{h_{R,n,l}}-\angle{h_{I,n,l}}
		That is to say, the optimal phase shift is obtained in closed form in the single-user scenario, and the phase of the composite channel equals that of the direct channel. Moreover, it can be observed from \ref{eq:R_k} and \ref{eq:z_k_expand} that the optimal phases of information and power waveform are both match to the composite channel as
		Therefore, the original problem \ref{op:su} is reduced to an waveform magnitude optimization problem
		Problem \ref{op:su_gp_1} is a Reversed Geometric Program which can be transformed to standard Geometric Program (GP). The idea is to decompose the information and power posynomials as sum of monomials, then derive their upper bounds using Arithmetic Mean-Geometric Mean (AM-GM) inequality \cite{Clerckx2018b,Chiang2005}. Let $z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)=\sum_{m=1}^{M}{g_{P,m}(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}$, problem \ref{op:su_gp_1} is equivalent to
		and then solve problem \ref{op:su_gp_2}. The algorithm is summarized in Algorithm \ref{al:fs_waveform}.
			\caption{FS-IRS: Waveform and Splitting Ratio}
			\label{al:fs_waveform}
				\State \textbf{Input} $P, \bar{R}, A_n \ \forall n$ by \ref{eq:h_{k,n}}
				\State \textbf{Initialize} $i \leftarrow 0$, $\boldsymbol{s}_{I/P}^{(0)}$, $\rho^{(0)}$
				\State $i \leftarrow i + 1$
				\State \textbf{Output} $\boldsymbol{s}_{I/P}^{\star}, \rho^{\star}, z^{\star}$

	\begin{subsection}{Frequency-Flat IRS}
		In contrast, frequency-flat IRS reflects all subbands equally with a DoF of $L$. We observe that
		\begin{equation}
			\begin{split}
				\lvert{h_{D,n}+\boldsymbol{v}_n^H\boldsymbol{\phi}}\rvert^2
				&=\lvert{h_{D,n}}\rvert^2+h_{D,n}^*\boldsymbol{v}_n^H\boldsymbol{\phi}+\boldsymbol{\phi}^H\boldsymbol{v}_n{h_{D,n}}+\boldsymbol{\phi}^H\boldsymbol{v}\boldsymbol{v}^H\boldsymbol{\phi}\\
				&=\bar{\boldsymbol{\phi}}^H\boldsymbol{R}_n\bar{\boldsymbol{\phi}}=\mathrm{Tr}(\boldsymbol{R}_n\bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H)=\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{\Phi})
			\end{split}
		\end{equation}
		where $t$ is an auxiliary variable with unit modulus and
		\begin{equation}\label{eq:R_n,phi}
			\boldsymbol{R}_n=
			\begin{bmatrix}
				\boldsymbol{v}_n\boldsymbol{v}_n^H & \boldsymbol{v}_n{h_{D,n}} \\
				h_{D,n}^*{\boldsymbol{v}_n^H}      & h_{D,n}^*{h_{D,n}}
			\end{bmatrix},
			\quad \bar{\boldsymbol{\phi}}=\
			\begin{bmatrix}
				\boldsymbol{\phi} \\
				t
			\end{bmatrix},
			\quad \boldsymbol{\Phi}=\bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H
		\end{equation}
		with $\boldsymbol{R}_n,\boldsymbol{\Phi} \in \mathbb{C}^{(L+1) \times (L+1)}$ and $\bar{\boldsymbol{\phi}} \in \mathbb{C}^{(L+1) \times 1}$. On top of this, the outer product of composite channel rewrites as
		\begin{equation}
			\boldsymbol{h}\boldsymbol{h}^H=\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}
		\end{equation}
		where $\boldsymbol{M}=[\boldsymbol{V}^H,\boldsymbol{h}_D]^H \in \mathbb{C}^{(L+1) \times N}$. To reduce the design complexity, we propose an suboptimal alternating optimization algorithm that iteratively updates the IRS phase shift, transmit waveform, and receive power splitting ratio with the others being fixed.

		\begin{subsubsection}{IRS Phase Shift Optimization}\label{se:fs_irs}

@@

				\caption{FF-IRS: IRS Phase Shift}

@@

					\State \textbf{Input} $\bar{R},Q,\boldsymbol{w}_I,\boldsymbol{w}_P,\rho,\sigma_n,\boldsymbol{R}_n,\boldsymbol{C}_{I/P,n} \ \forall n$ by \ref{eq:R_n,phi}, \ref{eq:C_{I/P,n}}
					\State \textbf{Initialize} $i \leftarrow 0,\boldsymbol{\Phi}^{(0)},t_{I/P,n}^{(0)}\ \forall n$ by \ref{eq:t}

@@

					\State $i \leftarrow i + 1$

@@

					\State Compute phase shift by $\theta_l=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$
					\State \textbf{Output} $\theta_l \ \forall l$

@@

		\begin{subsubsection}{Transmit Waveform Optimization}
			Consider the waveform optimization subproblem. Once $\boldsymbol{\Phi}$ and $\rho$ are obtained, introduce auxiliary variables
			\begin{equation}\label{eq:t'}
				t_{I/P,n}' = \boldsymbol{w}_{I/P}^H \boldsymbol{H}_n^* \boldsymbol{w}_{I/P} = \mathrm{Tr}(\boldsymbol{H}_n^*\boldsymbol{W}_{I/P})
			\end{equation}
			Therefore, \ref{eq:z_k_waveform} rewrites as
			\begin{equation}\label{eq:z_waveform}
				\begin{split}
					z(\boldsymbol{W}_I,\boldsymbol{W}_P)
					&=\frac{1}{2} \beta_2 \rho (t'_{I,0}+t'_{P,0})\\
					&\quad+\frac{3}{8} \beta_4 \rho^2 \left(2(t'_{I,0})^2 + \sum_{n=-N+1}^{N-1}{t'_{P,n}(t'_{P,n})^*}\right)\\
					&\quad+\frac{3}{2} \beta_4 \rho^2 t'_{I,0}t'_{P,0}
				\end{split}
			\end{equation}
			Since \ref{eq:z_waveform} and \ref{eq:z_irs} are in the same form, we reuse \ref{eq:t_{I,0}_square} -- \ref{eq:t_{I/P,0}} and bound \ref{eq:z_waveform} by replacing $t_{I/P,n}$ with $t_{I/P,n}'$ in \ref{eq:z_irs_approx}. Hence, problem \ref{op:su} is transformed to
			\begin{maxi!}
				{\boldsymbol{W}_I,\boldsymbol{W}_P}{\tilde{z}(\boldsymbol{W}_I,\boldsymbol{W}_P)}{\label{op:su_waveform}}{\label{eq:su_waveform_target}}
				\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)W_{I,n,n}\lvert h_n \rvert^2}{\sigma_n^2}\right)} \ge \bar{R}\label{eq:su_waveform_constraint}}
				\addConstraint{\frac{1}{2}\left(\mathrm{Tr}(\boldsymbol{W}_I)+\mathrm{Tr}(\boldsymbol{W}_P)\right) \le P}
				\addConstraint{\boldsymbol{W}_{I/P} \succeq 0}
				\addConstraint{\mathrm{rank}(\boldsymbol{W}_{I/P})=1\label{co:waveform_rank}}
			\end{maxi!}
			We then perform SDR and solve the optimal waveform matrix $\boldsymbol{W}_{I/P}^{\star}$ iteratively by interior-point method. $\boldsymbol{w}_I^{\star}$ and $\boldsymbol{w}_P^{\star}$ can also be extracted using randomized vectors $\boldsymbol{r}_q \in \mathbb{C}^{(L+1) \times 1}, \ q=1,\dots,Q$, whose entries are uniformly distributed on the unit circle $r_{q,n}=e^{j\xi}$, $\xi \sim \mathcal{U}[0,2\pi)$. The algorithm is summarized in Algorithm \ref{al:ff_waveform}.
			\begin{algorithm}
				\caption{FF-IRS: Transmit Waveform Optimization}
				\label{al:ff_waveform}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\bar{R},P,Q,\sigma_n,\boldsymbol{H}_n,\boldsymbol{R}_n \ \forall n$ by \ref{eq:R_n,phi}
					\State \textbf{Initialize} $i \leftarrow 0$, $\boldsymbol{W}_{I/P}^{(0)}$, $t_{I/P,n}^{\prime (0)} \ \forall n$
					\Repeat
					\State $i \leftarrow i + 1$
					\State Obtain waveform matrices $\boldsymbol{W}_{I/P}^{(i)}$ by solving problem \ref{op:su_waveform}
					\State Update auxiliary $t_{I/P,n}^{\prime (i)} \forall n$ by \ref{eq:t'} for SCA
					\Until $\lvert (z^{(i)}-z^{(i-1)}) / z^{(i)} \rvert \le \epsilon$
					\State Perform EVD $\boldsymbol{W}_{I/P}^{\star}=\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}^H$
					\State Generate random vectors $\boldsymbol{r}_q \ \forall q$ with entries uniformly distributed on the unit circle
					\State Construct candidate waveform vectors $\boldsymbol{w}_{I/P,r}=\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{W}_{I/P}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q$ and matrices $\boldsymbol{W}_{I/P,q}=\boldsymbol{w}_{I/P,q}\boldsymbol{w}_{I/P,q}^H  \ \forall q$
					\State Select best solution $\boldsymbol{W}_{I/P}^\star$ and $\boldsymbol{w}_{I/P}^\star$ for problem \ref{op:su_waveform}
					\State \textbf{Output} $\boldsymbol{w}_{I/P}^\star$
				\end{algorithmic}
			\end{algorithm}
		\end{subsubsection}

		\begin{subsubsection}{Receive Splitting Ratio Optimization}
			We then optimize the power splitting ratio $\rho$ for any fixed phase shift $\boldsymbol{\phi}$ and waveform $\boldsymbol{w}_{I/P}$. In this case, the output DC current is also expressed by \ref{eq:z_waveform} but as a function of $\rho$ with constant $t_{I/P,n}'$ defined in \ref{eq:t'}. Since $z(\rho)$ is a monotonically increasing function of $\rho \in [0, 1]$, we replace convex objective function $z(\rho)$ with affine $\rho$ and transform problem \ref{op:su} to
			\begin{maxi!}
				{\rho}{\rho}{\label{op:su_ratio}}{\label{eq:su_ratio_target}}
				\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert h_n w_n \rvert^2}{\sigma_n^2}\right)} \ge \bar{R}\label{eq:su_ratio_constraint}}
				\addConstraint{0 \le \rho \le 1}
			\end{maxi!}
			The optimal power splitting ratio $\rho^\star$ can be obtained from problem \ref{op:su_ratio}.
		\end{subsubsection}

		\begin{subsubsection}{WIT Initialization}
			To characterize the R-E region, we initialize the algorithm to WIT mode and reduce the rate constraint gradually to obtain the boundary points. Consider a rate maximization problem with given information waveform $\boldsymbol{w}_I$ and power splitting ratio $\rho = 0$ as
			\begin{maxi!}
				{\boldsymbol{\Phi}}{\sum_{n}{\log_2\left(1+\frac{\lvert{w}_{I,n}\rvert^2\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)}}{\label{op:su_irs_wit}}{}
				\addConstraint{\boldsymbol{\Phi}_{l,l}=1, \quad l=1,\dots,L+1}
				\addConstraint{\boldsymbol{\Phi}\succeq{0}}
				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1}
			\end{maxi!}
			Problem \ref{op:su_irs_wit} can be solved after SDR. Similar to section \ref{se:fs_irs}, a best solution $\bar{\boldsymbol{\phi}}^\star$ can be obtained via Gaussian randomization method and $\boldsymbol{\phi}^\star$ can be recovered by $\phi_l^\star=\phi_l^\star/\phi_{L+1}^\star, \ l=1,\dots,L$. After constructing composite channel $\boldsymbol{h}$ by \ref{eq:h_k}, we use water-filling algorithm and matched filter to obtain optimal power allocation $p_n^\star=\lvert w_{I,n} \rvert^2$ and beamforming phase $\psi_{I,n}^\star=-\bar{\psi}_n$, respectively. Therefore, the optimal information waveform at subband $n$ is
			\begin{equation}\label{eq:w_wit}
				w_{I,n}^\star=\sqrt{p_n^\star}e^{j \psi_{I,n}^\star}
			\end{equation}
			We update IRS phase shift by \ref{op:su_irs_wit} and information waveform by \ref{eq:w_wit} until convergence. The WIT initialization algorithm is summarized in \ref{al:ff_wit}.
			\begin{algorithm}
				\caption{FF-IRS: WIT Initialization}
				\label{al:ff_wit}
				\begin{algorithmic}[1]
					\State \textbf{Input} $P, Q, \boldsymbol{R}_n, \sigma_n \ \forall n$
					\State \textbf{Initialize} $i \leftarrow 0$, $\boldsymbol{w}_I^{(0)}$
					\Repeat
					\State $i \leftarrow i + 1$
					\State Obtain IRS matrix $\boldsymbol{\Phi}^{(i)}$ by solving problem \ref{op:su_irs_wit}
					\State Perform EVD $\boldsymbol{\Phi}^{(i)}=\boldsymbol{U}_{\boldsymbol{\Phi}^{(i)}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{(i)}}\boldsymbol{U}_{\boldsymbol{\Phi}^{(i)}}^H$
					\State Generate random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}) \ \forall q$
					\State Construct candidate IRS vectors $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}_{\boldsymbol{\Phi}^{(i)}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{(i)}}^{\frac{1}{2}}\boldsymbol{r}_q\right)}$ and matrices $\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H  \ \forall q$
					\State Select best solution $(\boldsymbol{\Phi}^{(i)})^\star$ and $(\boldsymbol{\phi}^{(i)})^\star$ for problem \ref{op:su_irs_wit}
					\State Update composite channel $(\boldsymbol{h}^{(i)})^\star$ by \ref{eq:h_k}
					\State Obtain optimal power allocation $p_n^{(i)} \ \forall n$ by water-filling algorithm
					\State Obtain optimal waveform phase $(\psi_{I,n}^{(i)})^\star \ \forall n$ by \ref{eq:psi}
					\State Update information waveform $(\boldsymbol{w}_I^{(i)})^\star$ by \ref{eq:w_wit}
					\Until $\lvert (R^{(i)}-R^{(i-1)}) / R^{(i)} \rvert \le \epsilon$
					\State \textbf{Output} $\boldsymbol{w}_I^\star, \boldsymbol{\phi}^\star$
				\end{algorithmic}
			\end{algorithm}
		\end{subsubsection}
	\end{subsection}
\end{section}

>>>>

\begin{section}{Single-User Optimization}
	Consider a single-user waveform and IRS optimization problem where $\boldsymbol{\alpha}=\boldsymbol{1}^{N \times 1}$. We characterize the rate-energy region through a current maximization problem subject to transmit power, rate, and IRS constraints
	\begin{maxi!}
			{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho}{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)}{\label{op:su}}{}
			\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
			\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert(h_{D,n}+\boldsymbol{v}_n^H\boldsymbol{\phi})w_{I,n}\rvert^2}{\sigma_n^2}\right)} \ge \bar{R}}
			\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}
			\addConstraint{0 \le \rho \le 1}
		\end{maxi!}
	Problem \ref{op:su} is intricate due to the non-convex objective function with coupled variables. To reduce the design complexity, we propose an suboptimal alternating optimization algorithm that iteratively updates the IRS phase shift, transmit waveform, and receive power splitting ratio iteratively.
	% In the next section, we propose waveform and phase shift design algorithms for frequency-flat and frequency-selective IRS, respectively.

	\begin{subsection}{IRS Phase Shift}
		\begin{subsubsection}{Frequency-Selective IRS}\label{se:fs_irs}
			Each element in frequency-selective IRS is expected to provide subband-dependent reflection coefficients. Hence, $\boldsymbol{\phi}_n$ replaces $\boldsymbol{\phi}$ in \ref{op:su} and the IRS has a total degree of freedom (DoF) of $NL$. Note that $\lvert{(h_{D,n}+\boldsymbol{v}_n^H\boldsymbol{\phi}_n)w_{I,n}}\rvert \le \lvert{h_{D,n}w_{I,n}}\rvert+\lvert{\boldsymbol{v}_n^H\boldsymbol{\phi}_n w_{I,n}}\rvert$ where the equality holds when the direct and IRS-aided links are aligned. Therefore, we choose the phase shift of element $l$ at subband $n$ as
			\begin{equation}\label{eq:theta}
				\theta_{n,l}^\star = \angle{h}_{D,n} - \angle{h_{R,n,l}}-\angle{h_{I,n,l}}
			\end{equation}
			That is to say, the optimal phase shift is obtained in closed form in the single-user scenario, and the phase of the composite channel equals that of the direct channel.
		\end{subsubsection}

		\begin{subsubsection}{Frequency-Flat IRS}
			In contrast, frequency-flat IRS reflects all subbands equally with a DoF of $L$. We observe that
			\begin{equation}
				\begin{split}
					\lvert{h_{D,n}+\boldsymbol{v}_n^H\boldsymbol{\phi}}\rvert^2
					&=\lvert{h_{D,n}}\rvert^2+h_{D,n}^*\boldsymbol{v}_n^H\boldsymbol{\phi}+\boldsymbol{\phi}^H\boldsymbol{v}_n{h_{D,n}}+\boldsymbol{\phi}^H\boldsymbol{v}\boldsymbol{v}^H\boldsymbol{\phi}\\
					&=\bar{\boldsymbol{\phi}}^H\boldsymbol{R}_n\bar{\boldsymbol{\phi}}=\mathrm{Tr}(\boldsymbol{R}_n\bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H)=\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{\Phi})
				\end{split}
			\end{equation}
			where $t$ is an auxiliary variable with unit modulus and
			\begin{equation}\label{eq:R_n,phi}
				\boldsymbol{R}_n=
				\begin{bmatrix}
					\boldsymbol{v}_n\boldsymbol{v}_n^H & \boldsymbol{v}_n{h_{D,n}} \\
					h_{D,n}^*{\boldsymbol{v}_n^H}      & h_{D,n}^*{h_{D,n}}
				\end{bmatrix},
				\quad \bar{\boldsymbol{\phi}}=\
				\begin{bmatrix}
					\boldsymbol{\phi} \\
					t
				\end{bmatrix},
				\quad \boldsymbol{\Phi}=\bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H
			\end{equation}
			with $\boldsymbol{R}_n,\boldsymbol{\Phi} \in \mathbb{C}^{(L+1) \times (L+1)}$ and $\bar{\boldsymbol{\phi}} \in \mathbb{C}^{(L+1) \times 1}$. On top of this, the outer product of composite channel rewrites as
			\begin{equation}\label{eq:M}
				\boldsymbol{h}\boldsymbol{h}^H=\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}
			\end{equation}
			where $\boldsymbol{M}=[\boldsymbol{V}^H,\boldsymbol{h}_D]^H \in \mathbb{C}^{(L+1) \times N}$.

@@

				\caption{FF-IRS: Phase Shift}

@@

					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_D,\boldsymbol{h}_I,\boldsymbol{h}_R,Q,\bar{R},\epsilon,\rho,\boldsymbol{w}_{I/P},\sigma_n \ \forall n$ by \ref{eq:R_n,phi}, \ref{eq:C_{I/P,n}}
					\State \textbf{Initialize} $i \gets 0,\boldsymbol{\Phi}^{(0)},t_{I/P,n}^{(0)}\ \forall n$ by \ref{eq:t}
					\State Construct $\boldsymbol{M},\boldsymbol{R}_n,\boldsymbol{C}_{I/P,n} \ \forall n$ by \ref{eq:M}, \ref{eq:R_n,phi}, \ref{eq:C_{I/P,n}}

@@

					\State $i \gets i + 1$

@@

					\State Compute phase shift by $\theta_l^\star=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$
					\State \textbf{Output} $\theta_l^\star \ \forall l$

@@

	\begin{subsection}{Waveform and Splitting Ratio}
		\begin{subsubsection}{Geometric Programming}
			Following \cite{Clerckx2018b}, it can be observed from \ref{eq:R_k} and \ref{eq:z_k_expand} that the optimal phases of information and power waveform are both match to the composite channel as
			Also, denote the waveform amplitude at subband $n$ as
			\begin{equation}\label{eq:s}
				s_{I/P,n} = \lvert w_{I/P,n} \rvert e^{j\psi_{I/P,n}}
			which is further collected into $\boldsymbol{s}_{I/P} \in \mathbb{C}^{N \times 1}$. Therefore, the original problem \ref{op:su} is reduced to an amplitude optimization problem
			Problem \ref{op:su_gp_1} is a reversed GP which can be transformed to standard GP. The idea is to decompose the information and power posynomials as sum of monomials, then derive their upper bounds using Arithmetic Mean-Geometric Mean (AM-GM) inequality \cite{Clerckx2018b,Chiang2005}. Let $z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)=\sum_{m=1}^{M}{g_{P,m}(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}$, problem \ref{op:su_gp_1} is equivalent to
			and then solve problem \ref{op:su_gp_2}. The GP algorithm is summarized in Algorithm \ref{al:waveform_split_ratio_gp}.
				\caption{GP: Waveform and Splitting Ratio}
				\label{al:waveform_split_ratio_gp}
					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h},P,\bar{R},\epsilon,\sigma_n \ \forall n$
					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{s}_{I/P}^{(0)}$, $\rho^{(0)}$
					\State Retrieve channel amplitude response $A_n \ \forall n$ by \ref{eq:h_{k,n}}
					\State $i \gets i + 1$
					\State Recover waveform $\boldsymbol{w}_{I/P}^{\star}$ by \ref{eq:psi} and \ref{eq:s}
					\State \textbf{Output} $\boldsymbol{w}_{I/P}^{\star}, \rho^{\star}$

		\begin{subsubsection}{Semi-Definite Relaxation}
			In this case, waveform and splitting ratio are updated iteratively until convergence.
			\begin{paragraph}{Transmit Waveform}
				Consider the waveform optimization subproblem. Once $\boldsymbol{\phi}$ and $\rho$ are obtained, introduce auxiliary variables
				\begin{equation}\label{eq:t'}
					t_{I/P,n}' = \boldsymbol{w}_{I/P}^H \boldsymbol{H}_n^* \boldsymbol{w}_{I/P} = \mathrm{Tr}(\boldsymbol{H}_n^*\boldsymbol{W}_{I/P})
				\end{equation}
				Therefore, \ref{eq:z_k_waveform} rewrites as
				\begin{equation}\label{eq:z_waveform}
					\begin{split}
						z(\boldsymbol{W}_I,\boldsymbol{W}_P)
						&=\frac{1}{2} \beta_2 \rho (t'_{I,0}+t'_{P,0})\\
						&\quad+\frac{3}{8} \beta_4 \rho^2 \left(2(t'_{I,0})^2 + \sum_{n=-N+1}^{N-1}{t'_{P,n}(t'_{P,n})^*}\right)\\
						&\quad+\frac{3}{2} \beta_4 \rho^2 t'_{I,0}t'_{P,0}
					\end{split}
				\end{equation}
				Since \ref{eq:z_waveform} and \ref{eq:z_irs} are in the same form, we reuse \ref{eq:t_{I,0}_square} -- \ref{eq:t_{I/P,0}} and bound \ref{eq:z_waveform} by replacing $t_{I/P,n}$ with $t_{I/P,n}'$ in \ref{eq:z_irs_approx}. Hence, problem \ref{op:su} is transformed to
				\begin{maxi!}
					{\boldsymbol{W}_I,\boldsymbol{W}_P}{\tilde{z}(\boldsymbol{W}_I,\boldsymbol{W}_P)}{\label{op:su_waveform}}{\label{eq:su_waveform_target}}
					\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)W_{I,n,n}\lvert h_n \rvert^2}{\sigma_n^2}\right)} \ge \bar{R}\label{eq:su_waveform_constraint}}
					\addConstraint{\frac{1}{2}\left(\mathrm{Tr}(\boldsymbol{W}_I)+\mathrm{Tr}(\boldsymbol{W}_P)\right) \le P}
					\addConstraint{\boldsymbol{W}_{I/P} \succeq 0}
					\addConstraint{\mathrm{rank}(\boldsymbol{W}_{I/P})=1\label{co:waveform_rank}}
				\end{maxi!}
				We then perform SDR and solve the optimal waveform matrix $\boldsymbol{W}_{I/P}^{\star}$ iteratively by interior-point method. $\boldsymbol{w}_I^{\star}$ and $\boldsymbol{w}_P^{\star}$ can also be extracted using randomized vectors $\boldsymbol{r}_q \in \mathbb{C}^{(L+1) \times 1}, \ q=1,\dots,Q$, whose entries are uniformly distributed on the unit circle $r_{q,n}=e^{j\xi}$, $\xi \sim \mathcal{U}[0,2\pi)$. The algorithm is summarized in Algorithm \ref{al:waveform_sdr}.
				\begin{algorithm}
					\caption{SDR: Transmit Waveform}
					\label{al:waveform_sdr}
					\begin{algorithmic}[1]
						\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_D,\boldsymbol{h}_I,\boldsymbol{h}_R,P,Q,\bar{R},\epsilon,\rho,\sigma_n \ \forall n$ by \ref{eq:R_n,phi}
						\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{W}_{I/P}^{(0)}$, $t_{I/P,n}^{\prime (0)} \ \forall n$ by \ref{eq:t'}
						\State Construct $\boldsymbol{H}_n,\boldsymbol{R}_n \ \forall n$ by \ref{eq:R_n,phi}
						\Repeat
						\State $i \gets i + 1$
						\State Obtain waveform matrices $\boldsymbol{W}_{I/P}^{(i)}$ by solving problem \ref{op:su_waveform}
						\State Update auxiliary $t_{I/P,n}^{\prime (i)} \forall n$ by \ref{eq:t'} for SCA
						\Until $\lvert (z^{(i)}-z^{(i-1)}) / z^{(i)} \rvert \le \epsilon$
						\State Perform EVD $\boldsymbol{W}_{I/P}^{\star}=\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}^H$
						\State Generate random vectors $\boldsymbol{r}_q \ \forall q$ with entries uniformly distributed on the unit circle
						\State Construct candidate waveform vectors $\boldsymbol{w}_{I/P,r}=\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{W}_{I/P}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q$ and matrices $\boldsymbol{W}_{I/P,q}=\boldsymbol{w}_{I/P,q}\boldsymbol{w}_{I/P,q}^H  \ \forall q$
						\State Select best solution $\boldsymbol{W}_{I/P}^\star$ and $\boldsymbol{w}_{I/P}^\star$ for problem \ref{op:su_waveform}
						\State \textbf{Output} $\boldsymbol{w}_{I/P}^\star$
					\end{algorithmic}
				\end{algorithm}
			\end{paragraph}

			\begin{paragraph}{Receive Splitting Ratio Optimization}
				We then optimize the power splitting ratio $\rho$ for any fixed phase shift $\boldsymbol{\phi}$ and waveform $\boldsymbol{w}_{I/P}$. In this case, the output DC current is also expressed in \ref{eq:z_waveform} but as a function of $\rho$ with constant $t_{I/P,n}'$ given by \ref{eq:t'}. Since $z(\rho)$ is a monotonically increasing function of $\rho \in [0, 1]$, we replace convex objective function $z(\rho)$ with affine $\rho$ and transform problem \ref{op:su} to
				\begin{maxi!}
					{\rho}{\rho}{\label{op:su_ratio}}{\label{eq:su_ratio_target}}
					\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert h_n w_n \rvert^2}{\sigma_n^2}\right)} \ge \bar{R}\label{eq:su_ratio_constraint}}
					\addConstraint{0 \le \rho \le 1}
				\end{maxi!}
				The optimal power splitting ratio $\rho^\star$ can be obtained by solving problem \ref{op:su_ratio}.
			\end{paragraph}
		\end{subsubsection}
	\end{subsection}
